---
title: "Data Science Challenge"
author: "Delermando Branquinho Filho"
date: "10 de novembro de 2016"
output: html_document
subtitle: Centrality metrics
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fist Challenge

In this challenge, suppose we are looking to do social network
analysis for prospective customers. We want to extract from
their social network a metric called "closeness centrality".
 
Centrality metrics try to approximate a measure of influence
of an individual within a social network. The distance between
any two vertices is their shortest path. The *farness*
of a given vertex *v* is the sum of all distances from each vertex
to *v*. Finally, the *closeness* of a vertex *v* is the inverse
of the *farness*.
 
The first part of the challenge is to rank the vertices in a given
graph by their *closeness*. The graph is provided in the attached
file; each line of the file consists of two vertex names separated by
a single space, representing an edge between those two nodes.

### Load Libraries

```{r, message=F, warning=F}
library(GGally)
library(network)
library(sna)
library(ggplot2)
```

*Seting seed for reproductble researsh*
```{r}
set.seed(3)
```

### Loadding Dataset

```{r}
myData <- as.matrix(read.table("D:/Data Science/Semantix/edges.dat", quote="\"", 
                    comment.char="", stringsAsFactors=FALSE))
```

### Creating Network Data

The nodes are numbered by one to number of nodes.

```{r}
net = rgraph(myData, mode = "graph")
net = network(net, directed = FALSE)
network.vertex.names(net) = 1:dim(myData)[1]
```

### Plotting
```{r, message=F, warning=F}
c.d   <- degree(net)
col<- as.integer(5*(c.d-min(c.d))/diff(range(c.d))+1)
palette <- c("purple","blue","green","yellow","orange","red")
g<-ggnet2(net, label = TRUE, label.color = "white",color = palette[col])
plot(g,vertex.color=palette[col],main="Degree Centrality",
     layout=layout.fruchterman.reingold)

```

## Second Challenge

The second part of the challenge is to create a RESTful web server
with endpoints to register edges and display the centrality of the graph.

### Degree 
The node degree is the number of relations (edges) of the nodes. 
```{r}
degree(net)
```

Betweenness centrality is even more important statistical property of a network. This is
applied in a lot of real-world problems, such as finding influential people in a social network,
finding crucial hubs in a computer network, finding border crossing points which have a
largest traffic or trade flow. 

```{r}
degree(net,cmode="indegree")
```


Closeness (farness) centrality indicates how long it will take for information from a given node to
reach other nodes in the network. The smaller the value, the more central role the node plays
in the network.

```{r}
degree(net,cmode="outdegree")
```

*Density*

The density of a graph is the number of existing edges divided by
the number of possible ones (assuming no duplicates or loops)
```{r}
gden(net,mode="graph")
```


Connectedness takes one or more graphs and returns the Krackhardt connectedness scores

```{r}
connectedness(net)
```

### Centrality
Centralization returns the centralization GLI (graph-level index) for a given graph in dat, given a (node) centrality measure FUN. Centralization follows Freeman's (1979) generalized definition of network centralization, and can be used with any properly defined centrality measure.
```{r}
centralization(net,degree,mode="graph")
```


### Betweenness Centrality
A measure of the degree to which a given node lies on the shortest paths (geodesics) between other nodes in the graph The centroid point of the map is:

```{r}
betweenness(net)
centralization(net,betweenness,mode="graph")
```

### Closeness Centrality
Closeness Centrality (CLC) is a category of measures that rate the centrality of a node by its closeness (distance) to other nodes. Closeness Centrality decreases if either the number of nodes reachable from the node in question decreases, or the distances between the nodes increases.

```{r}
closeness(net)
centralization(net,closeness,mode="graph")
```

*Egocentricity*
The egocentric network (or ego net) of vertex v in graph G is defined as the subgraph of G induced by v and its neighbors.

```{r}
newEgo <- ego.extract(net,6)
head(closeness(newEgo))
```

### REFERENCES
Alex, B. 1950. Communication patterns in task-oriented groups. J. Acoust. Soc. Am. 22 (6): 725-730.
Sabidussi, G. 1966. The centrality index of a graph. Psychometrika. 31: 581-603.
