---
title: "Desafio Data Science"
subtitle: "Centrality metrics"
author: "Delermando Branquinho Filho"
date: "10 de novembro de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fist Challenge

In this challenge, suppose we are looking to do social network
analysis for prospective customers. We want to extract from
their social network a metric called "closeness centrality".
 
Centrality metrics try to approximate a measure of influence
of an individual within a social network. The distance between
any two vertices is their shortest path. The *farness*
of a given vertex *v* is the sum of all distances from each vertex
to *v*. Finally, the *closeness* of a vertex *v* is the inverse
of the *farness*.
 
The first part of the challenge is to rank the vertices in a given
graph by their *closeness*. The graph is provided in the attached
file; each line of the file consists of two vertex names separated by
a single space, representing an edge between those two nodes.

### Load Libraries

```{r, message=F, warning=F}
library(GGally)
library(network)
library(sna)
library(ggplot2)

```

### Loadding Dataset

```{r}
myData <- as.matrix(read.table("D:/Data Science/Semantix/edges.dat", quote="\"", 
                    comment.char="", stringsAsFactors=FALSE))
```

### Creating Network Data F=Graph
```{r}

net = rgraph(myData, mode = "graph")
net = network(net, directed = FALSE)
network.vertex.names(net) = 1:dim(myData)[1]
```

### Plotting
```{r}

ggnet2(net,color = "blue", label = TRUE, label.color = "white")

```


## Second Challenge

The second part of the challenge is to create a RESTful web server
with endpoints to register edges and display the centrality of the graph.

### Degree 
The node degree is the number of relations (edges) of the nodes. 
```{r}
degree(net)
```

Betweenness centrality is even more important statistical property of a network. This is
applied in a lot of real-world problems, such as finding influential people in a social network,
finding crucial hubs in a computer network, finding border crossing points which have a
largest traffic or trade flow. 

```{r}
degree(net,cmode="indegree")
```


Closeness (farness) centrality indicates how long it will take for information from a given node to
reach other nodes in the network. The smaller the value, the more central role the node plays
in the network.

```{r}
degree(net,cmode="outdegree")
```

The centrol point of the map is:

```{r}
centralization(net,degree,cmode="indegree")

```


### REFERENCES
Alex, B. 1950. Communication patterns in task-oriented groups. J. Acoust. Soc. Am. 22 (6): 725-730.
Sabidussi, G. 1966. The centrality index of a graph. Psychometrika. 31: 581-603.
